---
title: "R Notebook"
output: html_notebook
---

```{r}
# Load necessary libraries
library(tidyverse)
source("helpers.R")
source("survey.R")
library("scales")

# Load dataset
rightWingData <- read.csv("sociopoliticalfrequency_tradeoff_right-merged.csv") %>% mutate(category = ifelse(category == "","survey",paste(category)),
                                                                                          poliParty = "Republican") 

leftWingData <- read.csv("sociopoliticalfreqtradeoffleft-merged.csv") %>% mutate(category = ifelse(category == "","survey",paste(category)),
                                                                                          poliParty = "Democrat") 

allData <- rbind(leftWingData,rightWingData)

bran_palette = c("#7ae7e5", "#fe5f55", "#B2A6DE", "#14342b", "#69385c")
frequencyPalette = c("#A1E8AF","#B2A6DE")
```

```{r}
test <- rightWingData %>% 
  filter(category=="survey")
```

```{r}
result <- extract_demographics(allData, "workerid", "response") %>% 
  filter(category == "survey") %>% 
  select(workerid,19:26) 
```


```{r}
library(tidyverse)
library(jsonlite)

# Read the CSV file

# Filter for critical trials
trial_data <- allData %>%
  filter(category == "trial", trial_type == "survey-html-form")

# Function to safely parse the response string
parse_response <- function(response_str) {
  # Replace single quotes with double quotes for valid JSON
  response_str <- gsub("'", '"', response_str)
  
  # Try to parse the JSON string
  tryCatch({
    fromJSON(response_str)
  }, error = function(e) {
    # Return NA values if parsing fails
    return(list(
      CNNBias = NA,
      FoxBias = NA,
      NPRBias = NA,
      realityBias = NA,
      valenceBias = NA,
      HuffPostBias = NA,
      BreitbartBias = NA,
      politicalBias = NA
    ))
  })
}

# Expand the response column
expanded_data <- trial_data %>%
  mutate(
    response_parsed = map(response, parse_response)
  ) %>%
  unnest_wider(response_parsed)

# If you want to keep only specific columns from the original data along with the new bias columns
final_data <- expanded_data %>%
  select(
    workerid, 
    item, 
    criticalTerm,
    CNNBias,
    FoxBias,
    NPRBias,
    realityBias,
    valenceBias,
    HuffPostBias,
    BreitbartBias,
    politicalBias
  )
```
```{r}
finalData <- merge(expanded_data,result,by="workerid")
```


```{r}
expanded_data %>% 
  group_by(valence) %>%
  summarize(meanVal = mean(as.numeric(valenceBias)))
```

```{r}
expanded_data %>% 
  group_by(wingBias,valence,poliParty) %>%
  summarize(meanCNN = mean(as.numeric(CNNBias)),
            meanFox = mean(as.numeric(FoxBias)),
            meanBB = mean(as.numeric(BreitbartBias)),
            meanHuff = mean(as.numeric(HuffPostBias)),
            meanVal = mean(as.numeric(valenceBias)),
            meanReal = mean(as.numeric(realityBias))) %>% 
  ggplot(aes(x=wingBias, y=meanVal, fill=valence)) + 
  geom_bar(stat="identity",position="dodge") + 
  theme_bw() + 
  labs(x = "Intended Bias", y="Mean Positivity Rating", fill = "Intended Valence") + 
  facet_wrap(~poliParty)
```


```{r}
expanded_data %>% 
  group_by(wingBias,politicalBias) %>%
  summarize(meanCNN = mean(as.numeric(CNNBias)),
            meanFox = mean(as.numeric(FoxBias)),
            meanBB = mean(as.numeric(BreitbartBias)),
            meanHuff = mean(as.numeric(HuffPostBias)),
            meanVal = mean(as.numeric(valenceBias)),
            meanReal = mean(as.numeric(realityBias)),
            meanPoliBias = mean(as.numeric(politicalBias))) %>% 
  ggplot(aes(x=wingBias, y=meanPoliBias, fill=wingBias)) + 
  geom_bar(stat="identity",position="dodge") + 
  theme_bw() + 
  labs(x = "Intended Bias", y="Mean Right-Wing rating", fill = "") + 
  #facet_wrap(~poliParty) + 
  ylim(0,100) +
  theme(legend.position = "none")
```

```{r}
expanded_data %>% 
  group_by(wingBias,criticalTerm,poliParty) %>%
  summarize(meanCNN = mean(as.numeric(CNNBias)),
            meanFox = mean(as.numeric(FoxBias)),
            meanBB = mean(as.numeric(BreitbartBias)),
            meanHuff = mean(as.numeric(HuffPostBias)),
            meanVal = mean(as.numeric(valenceBias)),
            meanReal = mean(as.numeric(realityBias)),
            meanPoliBias = mean(as.numeric(politicalBias))) %>% 
  ggplot(aes(x=criticalTerm, y=meanPoliBias, fill=wingBias)) + 
  geom_bar(stat="identity",position="dodge") + 
  theme_bw() + 
  labs(x = "Critical Term", y="Mean Right-Wing Rating", fill = "Intended Bias") + 
  facet_wrap(~poliParty) + 
  ylim(0,100) +
  coord_flip()
```


```{r}
expanded_data %>% 
  group_by(wingBias,criticalTerm,poliParty) %>%
  summarize(meanCNN = mean(as.numeric(CNNBias)),
            meanFox = mean(as.numeric(FoxBias)),
            meanBB = mean(as.numeric(BreitbartBias)),
            meanHuff = mean(as.numeric(HuffPostBias)),
            meanVal = mean(as.numeric(valenceBias)),
            meanReal = mean(as.numeric(realityBias)),
            meanPoliBias = mean(as.numeric(politicalBias))) %>% 
  ggplot(aes(x=criticalTerm, y=meanReal, fill=wingBias)) + 
  geom_bar(stat="identity",position="dodge") + 
  theme_bw() + 
  labs(x = "Critical Term", y="Mean AI-Generated Rating", fill = "Intended Bias") + 
  facet_wrap(~poliParty) + 
  ylim(0,100) +
  coord_flip()
```


```{r}
expanded_data %>% 
  group_by(criticalTerm,poliParty) %>%
  summarize(meanReal = mean(as.numeric(realityBias)),
            meanPoliBias = mean(as.numeric(politicalBias))) %>% 
  ggplot(aes(x=criticalTerm, y=meanReal, fill=poliParty)) + 
  geom_bar(stat="identity",position="dodge") + 
  theme_bw() + 
  labs(x = "Critical Term", y="Mean AI-Generated Rating") + 
  ylim(0,100) + 
  coord_flip()
```

```{r}
finalData %>% 
  group_by(wingBias,political) %>% 
  summarize(meanBias = mean(as.numeric(politicalBias))) %>% 
  ggplot(aes(x=wingBias,y=meanBias, group=1)) + 
  geom_point() + 
  geom_line() +
  facet_wrap(~political) + 
  theme(legend.position = "none") + 
  labs(x="Intended Bias", y="Mean Right-Wing Score") + 
  ylim(0,100)
```



```{r}
 summarize(mean_plural = mean(areRate), 
            CI.Low = ci.low(areRate),
            CI.High = ci.high(areRate))
```


```{r}
finalData %>% 
  mutate(ageGroup = ifelse(age <= 39, "younger", "older")) %>% 
  group_by(ageGroup,political,wingBias) %>% 
  summarize(meanBias = mean(as.numeric(politicalBias)),
            CI.Low = ci.low(as.numeric(politicalBias)),
            CI.High = ci.high(as.numeric(politicalBias))) %>% 
  mutate(YMin = meanBias - CI.Low, 
         YMax = meanBias + CI.High) %>% 
  ggplot(aes(x=wingBias,y=meanBias,group=1)) +
  geom_point() + 
  geom_line() + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) + 
  labs(x="Intended Bias", y="Mean Right-Wing Score") + 
  facet_grid(ageGroup~political) + 
  ylim(0,100) + 
  theme_bw()
```

```{r}
finalData %>% 
 # mutate(ageGroup = ifelse(age <= 39, "younger", "older")) %>% 
  group_by(poliParty,wingBias) %>% 
  summarize(meanBias = mean(as.numeric(politicalBias)),
            CI.Low = ci.low(as.numeric(politicalBias)),
            CI.High = ci.high(as.numeric(politicalBias))) %>% 
  mutate(YMin = meanBias - CI.Low, 
         YMax = meanBias + CI.High) %>% 
  ggplot(aes(x=wingBias,y=meanBias,fill=poliParty)) +
  geom_bar(stat="identity", position = position_dodge(width=0.9)) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25, position=position_dodge(width=0.9)) + 
  labs(x="Intended Bias", y="Mean Right-Wing Score", fill="Political Party") + 
  ylim(0,100) + 
  theme_bw() + 
  scale_fill_manual(values = bran_palette)
```


```{r}
finalData %>% 
  group_by(poliParty,wingBias) %>% 
  summarize(meanRt = mean(as.numeric(rt)),
            CI.Low = ci.low(as.numeric(rt)),
            CI.High = ci.high(as.numeric(rt))) %>% 
  mutate(YMin = meanRt - CI.Low, 
         YMax = meanRt + CI.High) %>% 
  ggplot(aes(x=wingBias,y=meanRt,fill=poliParty)) + 
  geom_bar(stat = "identity", position = position_dodge(width=0.9)) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25, position=position_dodge(width=0.9)) +
  labs(x="Intended Bias", y="Mean Reading Time (ms)", fill="Political Party") + 
  theme_bw() + 
  scale_fill_manual(values = bran_palette)
```







```{r}
indiBiasesData <- finalData %>% 
  group_by(workerid,poliParty,wingBias) %>% 
  summarize(meanBias = mean(as.numeric(politicalBias))) %>% 
  pivot_wider(names_from = wingBias, values_from = meanBias) %>% 
  summarize(individualDiff = right - left)
```
```{r}
finalDataEnhanced <- merge(finalData,indiBiasesData,by="workerid")
```


```{r}
finalDataEnhanced %>% 
  group_by(workerid,poliParty.x,individualDiff) %>% 
  summarize(meanRt = mean(as.numeric(rt)),
            CI.Low = ci.low(as.numeric(rt)),
            CI.High = ci.high(as.numeric(rt))) %>% 
  mutate(YMin = meanRt - CI.Low, 
         YMax = meanRt + CI.High) %>% 
  ggplot(aes(x=individualDiff, y=meanRt, color=poliParty.x)) +
  geom_point(stat="identity") + 
  geom_smooth(method="lm") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_vline(xintercept=2, linetype='dotted', col = 'purple')+
  labs(x="Individual Difference (MeanRight - MeanLeft)", y="Mean Reading Time (ms)", color="Political Party", shape="Intended Bias") + 
  theme_bw() + 
  scale_color_manual(values = bran_palette) + 
  scale_y_continuous(labels = label_comma()) + 
  ylim(0,220000)
```

```{r}
finalDataEnhanced %>% 
  group_by(wingBias, poliParty.x) %>% 
  summarize(meanBias = mean(as.numeric(politicalBias))) %>% 
  ggplot(aes(x=wingBias, y=meanBias,fill=wingBias)) + 
  geom_bar(stat="identity", position=position_dodge(width=0.9)) + 
  facet_wrap(~poliParty.x) + 
  theme_bw() + 
  scale_fill_manual(values = bran_palette) + 
  labs(x="Intended Bias", y = "Mean Right-Wing Rating") + 
  theme(legend.position = "none")
```




```{r}
finalDataExclusionTest <- finalDataEnhancedTest[abs(scale(finalDataEnhancedTest$meanRt)) <= 2.5, ]
```



# Hypthoesis Plotting

## Null Hypothesis 

Under the null hypothesis, we expect word learning to be unimpacted by both frequency and overt social beliefs

```{r}

frequencyLevels <- c("low","low","high","high")
socialAlignmentLevels <- c("aligned","disaligned","aligned","disaligned")
responseTimes <- c(550,550,550,550)

nullData <- data.frame(frequencyLevels,socialAlignmentLevels,responseTimes)
```

```{r}
nullData %>% 
  ggplot(aes(x=socialAlignmentLevels,y=responseTimes, fill=frequencyLevels)) + 
  geom_bar(stat="identity", position = position_dodge(width = 0.9)) + 
  ylim(0,700) + 
  labs(x="Sociopolitical alignment", y="Mean response time", fill="Token Frequency") + 
  theme_bw() + 
  scale_fill_manual(values = frequencyPalette)
```


## Hypothesis 1

Under the first alternative hypothesis, word learning is modulated purely by frequency effects, with social context playing no role

```{r}

frequencyLevels <- c("low","low","high","high")
socialAlignmentLevels <- c("aligned","disaligned","aligned","disaligned")
responseTimes <- c(600,600,520,520)

h1Data <- data.frame(frequencyLevels,socialAlignmentLevels,responseTimes)
```

```{r}
h1Data %>% 
  ggplot(aes(x=socialAlignmentLevels,y=responseTimes, fill=frequencyLevels)) + 
  geom_bar(stat="identity", position = position_dodge(width = 0.9)) + 
  ylim(0,700) + 
  labs(x="Sociopolitical alignment", y="Mean response time", fill="Token Frequency") + 
  theme_bw() + 
  scale_fill_manual(values = frequencyPalette)
```

## Hypothesis 2
Under alternative hypothesis two, only social beliefs above and beyond the level of frequency play a role in word-learning and memory encoding

### Sub-Hypothesis 1: Alignment-Enhanced memory encoding

```{r}

frequencyLevels <- c("low","low","high","high")
socialAlignmentLevels <- c("aligned","disaligned","aligned","disaligned")
responseTimes <- c(520,600,520,600)

h2Data <- data.frame(frequencyLevels,socialAlignmentLevels,responseTimes)
```

```{r}
h2Data %>% 
  ggplot(aes(x=socialAlignmentLevels,y=responseTimes, fill=frequencyLevels)) + 
  geom_bar(stat="identity", position = position_dodge(width = 0.9)) + 
  ylim(0,700) + 
  labs(x="Sociopolitical alignment", y="Mean response time", fill="Token Frequency") + 
  theme_bw() + 
  scale_fill_manual(values = frequencyPalette)
```


### Sub-Hypothesis 2: Alignment-Enhanced memory encoding

```{r}

frequencyLevels <- c("low","low","high","high")
socialAlignmentLevels <- c("aligned","disaligned","aligned","disaligned")
responseTimes <- c(600,520,600,520)

h2Data <- data.frame(frequencyLevels,socialAlignmentLevels,responseTimes)
```

```{r}
h2Data %>% 
  ggplot(aes(x=socialAlignmentLevels,y=responseTimes, fill=frequencyLevels)) + 
  geom_bar(stat="identity", position = position_dodge(width = 0.9)) + 
  ylim(0,700) + 
  labs(x="Sociopolitical alignment", y="Mean response time", fill="Token Frequency") + 
  theme_bw() + 
  scale_fill_manual(values = frequencyPalette)
```



## Hypothesis 3
Under hypothesis three (the hypothesis we are "hoping" to find, as it would indicate a tradeoff between cognitive pressures like frequency effects and social beliefs above and beyond that level), frequency effects will still show up, but will be modulated by social alignment

```{r}

frequencyLevels <- c("low","low","high","high")
socialAlignmentLevels <- c("aligned","disaligned","aligned","disaligned")
responseTimes <- c(540,630,500,600)

h3Data <- data.frame(frequencyLevels,socialAlignmentLevels,responseTimes)
```

```{r}
h3Data %>% 
  ggplot(aes(x=socialAlignmentLevels,y=responseTimes, fill=frequencyLevels)) + 
  geom_bar(stat="identity", position = position_dodge(width = 0.9)) + 
  ylim(0,700) + 
  labs(x="Sociopolitical alignment", y="Mean response time", fill="Token Frequency") + 
  theme_bw() + 
  scale_fill_manual(values = frequencyPalette)
```


```{r}

frequencyLevels <- c("low","low","high","high")
socialAlignmentLevels <- c("disaligned","aligned","disaligned","aligned")
responseTimes <- c(540,630,500,600)

h3Data <- data.frame(frequencyLevels,socialAlignmentLevels,responseTimes)
```

```{r}
h3Data %>% 
  ggplot(aes(x=socialAlignmentLevels,y=responseTimes, fill=frequencyLevels)) + 
  geom_bar(stat="identity", position = position_dodge(width = 0.9)) + 
  ylim(0,700) + 
  labs(x="Sociopolitical alignment", y="Mean response time", fill="Token Frequency") + 
  theme_bw() + 
  scale_fill_manual(values = frequencyPalette)
```

